External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-12 egpaper_for_review.tex
a

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
\item We achieve much better performance, visual quality, PSNR, SSIM, and speed for real image denoising problem.
\end{itemize}

@@

@@

\subsection{Comparing External PG Prior and Guided Internal Subspace Learning}

@@

\subsection{Adaptive Iterations of Different Noise Levels}
For real image denoising, we can perform well on images which have similar noise levels with the training dataset. How can we deal with the real noisy images whose noise levels are higher than the training dataset? The answer is to remove the noise by more iterations. The input image of each iteration is the recovered image of previous iteration. This makes sense since we can still view the recovered image as a real noisy image.

@@

\subsection{The Overall Algorithm}
%------------------------------------------------------------------------
\section{Experiments}
In this section, we perform real image image denoising experiments on three standard datasets. The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}. The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}. The third dataset is provided by the Commercial software Neat Image \cite{neatimage}. The second and third dataset do not have ground truth images.

@@

The PSNR and SSIM resluts are listed in table \ref{tab1}.
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  & 37.66 & 37.92 &  \textbf{ 38.46}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  & 0.9495  & 0.9625 &   \textbf{0.9677}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}\label{tab2}
\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 33.41  &  33.48 &  33.48  & 36.49   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.75 &  \textbf{ 37.04}
\\
\hline
SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9444 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9486 & 0.9485 &  \textbf{ 0.9509}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
\item We achieve much better performance on visual quality, PSNR, SSIM, and speed, than other competing methods for real image denoising problem.
\end{itemize}

@@

\subsection{Internal v.s. External Image Denoising}
The internal patch recurrence across multiple scales of a natural image has been successfully applied in many image restoration problems such as single image super-resolution \cite{Irani2009sr}, image denoising \cite{Irani2013separating}, blind image deblurring \cite{Irani2014deblur}, and image dehazing \cite{Irani2016dehazing}, etc. These work demonstrate that internal information is enough for denoising additive white Gaussian noise. The reason is that the AWGN noise is independent of the original clean images, and therefore it will be 缩小 when the image is scaled to smaller size. However, the real noise is dependent on the signal \cite{crosschannel2016} and it has fixed patterns from several main sources \cite{healey1994radiometric}. The internal information may be not enough for real image denoising problem. Noted that even in denoising AWGN, the introduce of external information will also improve the performance denoising methods \cite{luo2015adaptive}. In this paper, we demonstrate that for real noise which is signal dependent, it is essential to make use of external clean data.

@@

\subsection{What does External Data help the Internal Subspace Learning?}
The external data can help the internal learning in two ways. On one hand, it can guide the noisy image patches to be divided into correct subspaces through clustering. If we cluster the noisy patches in an automatical way, just like the PLE \cite{ple} did, the signal dependent noise would be hardly removed. With the help of clean external data, the noisy patches can be divided into correct subspaces. Besides, external data guided internal clustering is much more efficient than directly clustering the noisy data due to the time consuming fitting procedure. On the other hand, due to the correct division of internal noisy data, the dictionary and paranters for subspace learning could be more adaptive to the testing real noisy image. Hence, it would achieve better denoising performance than the methods only using the external information.

\subsection{The Internal Subspace is truly the subspace of external space}
Plot a Figure to demonstrate the data distributed in external space and the assigned internal subspace. The internal subspace is only a subspace of the external space. Hence, if we use the external data to perform denoising, the performance would be limited due to the dependence of noise on signal. If we combine the external and internal data for subspace learning, the learned subspace would be too generative and would therefore not specifically suitable for the testing data.

@@

\subsection{Iterative Regularization}
Perfoming image denoising in one iteration is not enough for real noise since the noise is signal dependent. The removed noise in one iteration is largely dependent on the signal. Therefore, it is essential to add back some residuals removed in this iteration for the denoising of the next iteration.

\subsection{Effectively dealing with different noisy images}
For real image denoising, we can perform well on images which have similar noise levels with the training dataset. How can we deal with the real noisy images whose noise levels are higher than the training dataset? The answer is to remove the noise by more iterations. The input image of each iteration is the recovered image of previous iteration. This makes sense since we can still view the recovered image as a real noisy image.

@@

\subsection{The Overall Algorithm}

%------------------------------------------------------------------------
\section{Experiments}
In this section, we perform real image image denoising experiments on three standard datasets. The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}. The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}. The third dataset is provided by the Commercial software Neat Image \cite{neatimage}. The second and third dataset do not have ground truth images.

@@

The PSNR and SSIM resluts are listed in table \ref{tab1}.
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  &     & 38.07 &  \textbf{ 38.46}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  &     & 0.9625 &   \textbf{0.9677}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}\label{tab2}
\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 33.41  &  33.48 &  33.48  & 34.32   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.73 &  \textbf{ 37.04}
\\
\hline
SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9113 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9479 & 0.9419 &  \textbf{ 0.9509}
\\
\hline
\end{tabular}
\end{center}
\end{table*}
